---
title: "OpenFace Analysis"
author: "Julianna Calabrese"
date: 'Last updated  `r format(Sys.time(), "%d %B %Y")`'
output:
  rmdformats::robobook:
editor_options: 
  chunk_output_type: console
---

```{r set-options, echo=FALSE, cache=FALSE}
options(width = 9999)
```

# Introduction

At this point, OpenFace has analyzed all the videos, the .csv files have been run through openfaceprocess_pt1 and openfaceprocess_pt2, and hopefully now the data is ready for analysis.

```{r Libraries, include=FALSE}
# Load in packages

library(psych)
library(dplyr)
library(tidyverse)
library(lessR)
library(purrr)
library(reshape2)
library(panelr)
library(data.table)
library(haven)
library(foreign)
library(foreach)
library(zoo)
library(report)
library(DiagrammeR)
library(grDevices)
library(sjPlot)
library(lmerTest)
library(brms)
library(BVAR)
library(bvartools)
library(tsm)
library(vars)
library(astsa)
library(mFilter)
library(xts)
library(mlVAR)
library(rmdformats)
library(crosstalk)
library(kableExtra)
library(pairwiseComparisons)
library(foreign)
library(Hmisc)
library(arm)
library(corrplot)
library(emmeans)
library(broom)
library(ICSNP)
library(rstatix)
library(ggpubr)
options(scipen=99999)
graphics.off()
```

```{r include=FALSE}
# Read in data
fit_dat_smooth <- read.csv("~/firstyearproject/openfaceprocess_pt2_smooth.csv")

# Are there any NA values?
colSums(is.na(fit_dat_smooth))

# How many IDs are there?
length(unique(fit_dat_smooth$ID))

# Look at clipIDs
print(unique(fit_dat_smooth$ID))

# Is it the right class?
class(fit_dat_smooth$AU01_r_daughter) # Should be numeric

# Remove ID 164 because you should...
fit_dat_smooth <- fit_dat_smooth[fit_dat_smooth$ID != 164, ]

# Look at clipIDs
print(unique(fit_dat_smooth$ID))
```

# OpenFace/FPPC Correlations

```{r include=FALSE}
# Read in survey data
survey <- read_sav("~/firstyearproject/FinalDissertationData.sav")

survey <- survey %>% 
  dplyr::select(ends_with(c("ID", "_HI", "_IN", "_LW", "TOTAV", "TOTE")))

# Merge OpenFace data with FPPC data
merge <- merge(fit_dat_smooth, survey)

# Get rid of AUs we don't need the absence/presence variables
merge <- merge %>% 
  dplyr::select(-contains(c("01", "02", "07", "14", "15", 
                     "17", "20", "23", "26", "45", "_c_",
                     "pADHDID", "cADHDID", "SCID", "cSHvalid"))) 
                      #idk how those got in there
 
# Make a dataframe for daughter variables
daughter <- merge %>% 
  dplyr::select(contains(c("_r_daughter", "T_")))

# Make a dataframe for mother variables
mother <- merge %>% 
  dplyr::select(contains(c("_r_mother", "M_")))

# Make one with both mothers and daughters
corr <- merge %>% 
  dplyr::select(-contains(c("ID", "GROUP", "grp", "frame")))
```

```{r include=FALSE}
average <- merge %>% 
  dplyr::select(-contains(c("grp", "frame")))

average <- average %>% 
  group_by(ID, GROUP) %>% 
  summarise_all(mean)

average_merge <- merge(average, survey)

average_merge <- average_merge %>% 
  dplyr::select(-contains(c("01", "02", "07", "14", "15", 
                     "17", "20", "23", "26", "45", "_c_",
                     "pADHDID", "cADHDID", "SCID", "cSHvalid")))

average_merge <- average_merge %>% 
  dplyr::select(-contains(c("ID", "GROUP", "grp", "frame")))

# Reorganize the dataframe
# so average_merge and corr are in the same order
average_merge <- average_merge %>%
  dplyr::select(-M_HI, everything())

average_merge <- average_merge %>%
  dplyr::select(-T_HI, everything())

average_merge <- average_merge %>%
  dplyr::select(-M_TOTAV, everything())

average_merge <- average_merge %>%
  dplyr::select(-T_TOTAV, everything())

average_merge <- average_merge %>%
  dplyr::select(-M_TOTE, everything())

average_merge <- average_merge %>%
  dplyr::select(-T_TOTE, everything())
```

```{r}
glimpse(average_merge)
arm::corrplot(average_merge, color=TRUE)
```

```{r include=FALSE}
# Goes off the page
tab_corr(average_merge,
         title = "FPPC/AFEC Total Correlation Table",
         triangle = "lower",
         digits = 2,
         p.numeric = FALSE,
         remove.spaces = TRUE,
         use.viewer = TRUE)
```

```{r include=FALSE}
rm(list = setdiff(ls(), "fit_dat_smooth"))
```

# Average affect intensity

```{r include=FALSE}
# Read in data
fit_dat_smooth <- read.csv("~/firstyearproject/openfaceprocess_pt2_smooth.csv")

here <- fit_dat_smooth %>%
  dplyr::group_by(GROUP) %>%
  dplyr::summarise_at(vars(-ID, -grp, -frame_mother, -frame_daughter), 
                           #-AgeChild), 
                      funs(mean(., na.rm=TRUE)))

# Want to remove the extra columns?
here <- here %>%
  dplyr::select(-contains(c("AU01_r_mother", "AU02_r_mother", "AU07_r_mother",
                "AU14_r_mother", "AU15_r_mother", "AU17_r_mother",
                "AU20_r_mother", "AU23_r_mother", "AU26_r_mother",
                "AU45_r_mother", "AU01_r_daughter", "AU02_r_daughter", 
                "AU07_r_daughter", "AU14_r_daughter", "AU15_r_daughter", 
                "AU17_r_daughter", "AU20_r_daughter", "AU23_r_daughter", 
                "AU26_r_daughter", "AU45_r_daughter")))

here <- here %>% 
  dplyr::select(-contains("_c_"))

mother <- here %>% 
  dplyr::select(-contains("daughter"))
  
daughter <- here %>% 
  dplyr::select(-contains("mother"))

here <- reshape2::melt(here, id.var = "GROUP")
mother <- reshape2::melt(mother, id.var = "GROUP")
daughter <- reshape2::melt(daughter, id.var = "GROUP")

mother$variable <- as.character(mother$variable)
daughter$variable <- as.character(daughter$variable)

mother$GROUP[mother$GROUP == "depressed"] <- "Depressed"
mother$GROUP[mother$GROUP == "self-harm"] <- "Self-Harm"
mother$GROUP[mother$GROUP == "control"] <- "Control"

mother$variable[mother$variable == "AU04_r_mother"] <- "AU04"
mother$variable[mother$variable == "AU05_r_mother"] <- "AU05"
mother$variable[mother$variable == "AU06_r_mother"] <- "AU06"
mother$variable[mother$variable == "AU09_r_mother"] <- "AU09"
mother$variable[mother$variable == "AU10_r_mother"] <- "AU10"
mother$variable[mother$variable == "AU12_r_mother"] <- "AU12"
mother$variable[mother$variable == "AU25_r_mother"] <- "AU25"

daughter$GROUP[daughter$GROUP == "depressed"] <- "Depressed"
daughter$GROUP[daughter$GROUP == "self-harm"] <- "Self-Harm"
daughter$GROUP[daughter$GROUP == "control"] <- "Control"

daughter$variable[daughter$variable == "AU04_r_daughter"] <- "AU04"
daughter$variable[daughter$variable == "AU05_r_daughter"] <- "AU05"
daughter$variable[daughter$variable == "AU06_r_daughter"] <- "AU06"
daughter$variable[daughter$variable == "AU09_r_daughter"] <- "AU09"
daughter$variable[daughter$variable == "AU10_r_daughter"] <- "AU10"
daughter$variable[daughter$variable == "AU12_r_daughter"] <- "AU12"
daughter$variable[daughter$variable == "AU25_r_daughter"] <- "AU25"
```

```{r echo=FALSE}
ggplot(mother, aes(x=variable, y=value, fill=GROUP)) + 
  geom_col() + 
  #coord_flip() +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1)) +
  ylab(" ") + xlab(" ") + ggtitle("Mean Action Unit values for mothers")

ggplot(daughter, aes(x=variable, y=value, fill=GROUP)) + 
  geom_col() + 
  #coord_flip() +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1)) +
  ylab(" ") + xlab(" ") + ggtitle("Mean Action Unit values for daughters")
```

```{r include=FALSE}
rm(list = setdiff(ls(), "fit_dat_smooth"))
```

# Dyadic correspondence: Nate's models

C1 --> control versus (depressed+self-harm)

C2 --> depressed versus self-harm

## Nate's positive emotion model

```{r echo=TRUE}
Nates_old_data <- read.csv("~/firstyearproject/Nates_old_data.csv")

# Contrast matrix
mat1 <- rbind(c(1, -0.5, -0.5), # control vs. (depressed + self-harm) / 2
             c(0, -1, 1))       # depressed vs. self-harm
cMat1 <- MASS::ginv(mat1)
```

```{r echo=TRUE}
# Positive affect model
fit_posFR <- lmer(pos_mother ~ pos_daughter * GROUP + (pos_daughter | ID),
                  data = Nates_old_data,
                  contrasts = list(GROUP = cMat1))
```

```{r echo=FALSE}
fit_posFR <- lmer(pos_mother ~ pos_daughter * GROUP + (pos_daughter | ID),
                  data = Nates_old_data,
                  contrasts = list(GROUP = cMat1))

tab_model(fit_posFR,
          title = "Nate's model, predict mother's positive emotion with daughter's positive emotion",
          pred.labels = c("Intercept's intercept", "Slope's intercept", 
                          "Intercept C1", "Intercept C2", "Slope C1", "Slope C2"),
          show.est = TRUE, string.est = "Coefficient",
          show.stat = TRUE, string.stat = "t",
          p.threshold = 0.05, p.style=c("numeric"),
          show.ci = FALSE, show.se = TRUE, string.se = "SE",
          digits = 2, digits.p = 3, emph.p = TRUE, wrap.labels=25,
          order.terms = c(1, 3, 4, 2, 5, 6))
```

## Nate's negative emotion model

```{echo=TRUE}
# Negative affect model
fit_negFR <- lmer(neg_mother ~ neg_daughter * GROUP + (neg_daughter | ID),
                  data = Nates_old_data,
                  contrasts = list(GROUP = cMat1))
```

```{r echo=FALSE}
# Negative affect model
fit_negFR <- lmer(neg_mother ~ neg_daughter * GROUP + (neg_daughter | ID),
                  data = Nates_old_data,
                  contrasts = list(GROUP = cMat1))

tab_model(fit_negFR,
          title = "Nate's model, predict mother's negative emotion with daughter's negative emotion",
          pred.labels = c("Intercept's intercept", "Slope's intercept", 
                          "Intercept C1", "Intercept C2", "Slope C1", "Slope C2"),
          show.est = TRUE, string.est = "Coefficient",
          show.stat = TRUE, string.stat = "t",
          p.threshold = 0.05, p.style=c("numeric"),
          show.ci = FALSE, show.se = TRUE, string.se = "SE",
          digits = 2, digits.p = 3, emph.p = TRUE, wrap.labels=25,
          order.terms = c(1, 3, 4, 2, 5, 6))
```

```{r include=FALSE}
round(coef(summary(fit_posFR)), 3)
round(coef(summary(fit_negFR)), 3)
```

# Dyadic correspondence: OpenFace models

```{r include=FALSE}
# Read in data
fit_dat_smooth <- read.csv("~/firstyearproject/openfaceprocess_pt2_smooth.csv")
```

```{r echo=TRUE}
# Contrast matrix
mat1 <- rbind(c(1, -0.5, -0.5), # control vs. (depressed + self-harm) / 2
             c(0, -1, 1))       # depressed vs. self-harm
cMat1 <- MASS::ginv(mat1)
```

Positive emotion AUs: AU06, AU12, and AU25.

## OpenFace positive emotion models

```{r echo=TRUE}
mod06 <- lmer(AU06_r_mother ~ AU06_r_daughter * GROUP + (AU06_r_daughter | ID),
                  data = fit_dat_smooth,
                  contrasts = list(GROUP = cMat1))
```

```{r echo=FALSE}
mod06 <- lmer(AU06_r_mother ~ AU06_r_daughter * GROUP + (AU06_r_daughter | ID),
                  data = fit_dat_smooth,
                  contrasts = list(GROUP = cMat1))

tab_model(mod06,
          pred.labels = c("Intercept's intercept", "Slope's intercept", 
                          "Intercept C1", "Intercept C2", "Slope C1", "Slope C2"),
          dv.labels = "Predicting mother AU06",
          title = NULL, 
          show.est = TRUE, string.est = "Coefficient",
          show.stat = TRUE, string.stat = "t",
          p.threshold = 0.05, p.style=c("numeric"),
          show.ci = FALSE, show.se = TRUE, string.se = "SE",
          digits = 2, digits.p = 3, emph.p = TRUE, wrap.labels=25,
          order.terms = c(1, 3, 4, 2, 5, 6))
```

```{echo=TRUE}
mod12 <- lmer(AU12_r_mother ~ AU12_r_daughter * GROUP + (AU12_r_daughter | ID),
                  data = fit_dat_smooth,
                  contrasts = list(GROUP = cMat1))
```

```{r echo=FALSE}
mod12 <- lmer(AU12_r_mother ~ AU12_r_daughter * GROUP + (AU12_r_daughter | ID),
                  data = fit_dat_smooth,
                  contrasts = list(GROUP = cMat1))

tab_model(mod12,
          pred.labels = c("Intercept's intercept", "Slope's intercept", 
                          "Intercept C1", "Intercept C2", "Slope C1", "Slope C2"),
          dv.labels = "Predicting mother AU12",
          title = NULL, 
          show.est = TRUE, string.est = "Coefficient",
          show.stat = TRUE, string.stat = "t",
          p.threshold = 0.05, p.style=c("numeric"),
          show.ci = FALSE, show.se = TRUE, string.se = "SE",
          digits = 2, digits.p = 3, emph.p = TRUE, wrap.labels=25,
          order.terms = c(1, 3, 4, 2, 5, 6))
```

```{echo=TRUE}
mod25 <- lmer(AU25_r_mother ~ AU25_r_daughter * GROUP + (AU25_r_daughter | ID),
                  data = fit_dat_smooth,
                  contrasts = list(GROUP = cMat1))
```

```{r echo=FALSE}
mod25 <- lmer(AU25_r_mother ~ AU25_r_daughter * GROUP + (AU25_r_daughter | ID),
                  data = fit_dat_smooth,
                  contrasts = list(GROUP = cMat1))

tab_model(mod25,
          pred.labels = c("Intercept's intercept", "Slope's intercept", 
                          "Intercept C1", "Intercept C2", "Slope C1", "Slope C2"),
          dv.labels = "Predicting mother AU25",
          title = NULL, 
          show.est = TRUE, string.est = "Coefficient",
          show.stat = TRUE, string.stat = "t",
          p.threshold = 0.05, p.style=c("numeric"),
          show.ci = FALSE, show.se = TRUE, string.se = "SE",
          digits = 2, digits.p = 3, emph.p = TRUE, wrap.labels=25,
          order.terms = c(1, 3, 4, 2, 5, 6))
```

```{r include=FALSE}
round(coef(summary(fit_posFR)), 3)
round(coef(summary(mod06)), 3)
round(coef(summary(mod12)), 3)
round(coef(summary(mod25)), 3)
```

## OpenFace negative emotion models

Negative emotion AUs: AU04, AU05, AU09, and AU10. 

```{r echo=TRUE}
mod04 <- lmer(AU04_r_mother ~ AU04_r_daughter * GROUP + (AU04_r_daughter | ID),
                  data = fit_dat_smooth,
                  contrasts = list(GROUP = cMat1))
```

```{r echo=FALSE}
mod04 <- lmer(AU04_r_mother ~ AU04_r_daughter * GROUP + (AU04_r_daughter | ID),
                  data = fit_dat_smooth,
                  contrasts = list(GROUP = cMat1))

tab_model(mod04,
          pred.labels = c("Intercept's intercept", "Slope's intercept", 
                          "Intercept C1", "Intercept C2", "Slope C1", "Slope C2"),
          dv.labels = "Predicting mother AU04",
          title = NULL, 
          show.est = TRUE, string.est = "Coefficient",
          show.stat = TRUE, string.stat = "t",
          p.threshold = 0.05, p.style=c("numeric"),
          show.ci = FALSE, show.se = TRUE, string.se = "SE",
          digits = 2, digits.p = 3, emph.p = TRUE, wrap.labels=25,
          order.terms = c(1, 3, 4, 2, 5, 6))
```

```{r echo=TRUE}
mod05 <- lmer(AU05_r_mother ~ AU05_r_daughter * GROUP + (AU05_r_daughter | ID),
                  data = fit_dat_smooth,
                  contrasts = list(GROUP = cMat1))
```

```{r echo=FALSE}
mod05 <- lmer(AU05_r_mother ~ AU05_r_daughter * GROUP + (AU05_r_daughter | ID),
                  data = fit_dat_smooth,
                  contrasts = list(GROUP = cMat1))

tab_model(mod05,
          pred.labels = c("Intercept's intercept", "Slope's intercept", 
                          "Intercept C1", "Intercept C2", "Slope C1", "Slope C2"),
          dv.labels = "Predicting mother AU05",
          title = NULL, 
          show.est = TRUE, string.est = "Coefficient",
          show.stat = TRUE, string.stat = "t",
          p.threshold = 0.05, p.style=c("numeric"),
          show.ci = FALSE, show.se = TRUE, string.se = "SE",
          digits = 2, digits.p = 3, emph.p = TRUE, wrap.labels=25,
          order.terms = c(1, 3, 4, 2, 5, 6))
```

```{r echo=TRUE}
mod09 <- lmer(AU09_r_mother ~ AU09_r_daughter * GROUP + (AU09_r_daughter | ID),
                  data = fit_dat_smooth,
                  contrasts = list(GROUP = cMat1))
```

```{r echo=FALSE}
mod09 <- lmer(AU09_r_mother ~ AU09_r_daughter * GROUP + (AU09_r_daughter | ID),
                  data = fit_dat_smooth,
                  contrasts = list(GROUP = cMat1))

tab_model(mod09,
          pred.labels = c("Intercept's intercept", "Slope's intercept", 
                          "Intercept C1", "Intercept C2", "Slope C1", "Slope C2"),
          dv.labels = "Predicting mother AU09",
          title = NULL, 
          show.est = TRUE, string.est = "Coefficient",
          show.stat = TRUE, string.stat = "t",
          p.threshold = 0.05, p.style=c("numeric"),
          show.ci = FALSE, show.se = TRUE, string.se = "SE",
          digits = 2, digits.p = 3, emph.p = TRUE, wrap.labels=25,
          order.terms = c(1, 3, 4, 2, 5, 6))
```

```{r echo=TRUE}
mod10 <- lmer(AU10_r_mother ~ AU10_r_daughter * GROUP + (AU10_r_daughter | ID),
                  data = fit_dat_smooth,
                  contrasts = list(GROUP = cMat1))
```

```{r echo=FALSE}
mod10 <- lmer(AU10_r_mother ~ AU10_r_daughter * GROUP + (AU10_r_daughter | ID),
                  data = fit_dat_smooth,
                  contrasts = list(GROUP = cMat1))

tab_model(mod10,
          pred.labels = c("Intercept's intercept", "Slope's intercept", 
                          "Intercept C1", "Intercept C2", "Slope C1", "Slope C2"),
          dv.labels = "Predicting mother AU10",
          title = NULL, 
          show.est = TRUE, string.est = "Coefficient",
          show.stat = TRUE, string.stat = "t",
          p.threshold = 0.05, p.style=c("numeric"),
          show.ci = FALSE, show.se = TRUE, string.se = "SE",
          digits = 2, digits.p = 3, emph.p = TRUE, wrap.labels=25,
          order.terms = c(1, 3, 4, 2, 5, 6))
```

```{r include=FALSE}
round(coef(summary(fit_negFR)), 3)
round(coef(summary(mod04)), 3)
round(coef(summary(mod05)), 3)
round(coef(summary(mod09)), 3)
round(coef(summary(mod10)), 3)
```

# Effect of age on dyadic correspondence

```{r include=FALSE}
# Read in data
use_dat <- read.csv("~/firstyearproject/openfaceprocess_pt2_smooth.csv")

# Remove ID 164 because you should...
use_dat <- use_dat[use_dat$ID != 164, ]

# Look at clipIDs
print(unique(use_dat$ID))

# Are there any NA values?
colSums(is.na(use_dat))

# How many IDs are there?
length(unique(use_dat$ID))

# Look at clipIDs
print(unique(use_dat$ID))

# Is it the right class?
class(use_dat$AU01_r_daughter) # Should be numeric

# Read in survey data
survey <- read_sav("~/firstyearproject/FinalDissertationData.sav")
surveyage <- survey[c("ID", "AgeChild")]
rm(survey)

# Merge with use_dat
use_dat <- merge(use_dat, surveyage, by="ID")
rm(surveyage)
```

```{r include=FALSE}
# Effect of age on positive affect correspondence
# Non-smoothed data used here
cor_dat <- use_dat %>%
  #merge(surveyage, by = "ID") %>%
  dplyr::group_by(ID, GROUP) %>%
  dplyr::filter(ID!="164") %>% # this dyad had only 3 10-second clips
  dplyr::summarize(AU04 = cor(AU04_r_mother, AU04_r_daughter, use="complete.obs"),
            AU05 = cor(AU05_r_mother, AU05_r_daughter, use="complete.obs"),
            AU06 = cor(AU06_r_mother, AU06_r_daughter, use="complete.obs"),
            AU09 = cor(AU09_r_mother, AU09_r_daughter, use="complete.obs"),
            AU10 = cor(AU10_r_mother, AU10_r_daughter, use="complete.obs"),
            AU12 = cor(AU12_r_mother, AU12_r_daughter, use="complete.obs"),
            AU25 = cor(AU25_r_mother, AU25_r_daughter, use="complete.obs"),
            age = first(AgeChild))
rm(use_dat)
```

## Action Unit 4

```{r}
# Correlation of child age with AU04 correspondence
cor_p <- with(cor_dat, cor.test(age, AU04))
qplot(x = age, y = AU04, data = cor_dat,
      geom = c("point", "smooth"), method = "lm",
      xlab = "Daughter Age (Years)",
      ylab = "Action Unit 4 Correspondence") +
  annotate("text", x = 14, y = .5,
           label = paste0("r = ", round(cor_p$estimate, 2), 
                          "\np = ", round(cor_p$p.value, 3)), size = 5) +
  scale_x_continuous(breaks = 13:18) +
  theme_minimal(base_size = 18)

# Look at age-positive affect correspondence correlations within groups 
with(cor_dat %>% filter(GROUP=="control"), cor.test(AU04, age, method = "pearson"))
with(cor_dat %>% filter(GROUP=="depressed"), cor.test(AU04, age, method = "pearson"))
with(cor_dat %>% filter(GROUP=="self-harm"), cor.test(AU04, age, method = "pearson"))
```

```{r}
cor_p <- with(cor_dat, cor.test(age, AU04))
qplot(x = age, y = AU04, data = cor_dat, color = GROUP,
      geom = c("point", "smooth"), method = "lm",
      xlab = "Daughter Age (Years)",
      ylab = "Action Unit 4 Correspondence")
```

## Action Unit 5

```{r}
# Correlation of child age with AU05 correspondence
cor_p <- with(cor_dat, cor.test(age, AU05))
qplot(x = age, y = AU05, data = cor_dat,
      geom = c("point", "smooth"), method = "lm",
      xlab = "Daughter Age (Years)",
      ylab = "Action Unit 5 Correspondence") +
  annotate("text", x = 13.5, y = .6,
           label = paste0("r = ", round(cor_p$estimate, 2), 
                          "\np = ", round(cor_p$p.value, 3)), size = 5) +
  scale_x_continuous(breaks = 13:18) +
  theme_minimal(base_size = 18)

# Look at age-positive affect correspondence correlations within groups 
with(cor_dat %>% filter(GROUP=="control"), cor.test(AU05, age, method = "pearson"))
with(cor_dat %>% filter(GROUP=="depressed"), cor.test(AU05, age, method = "pearson"))
with(cor_dat %>% filter(GROUP=="self-harm"), cor.test(AU05, age, method = "pearson"))
```

```{r}
cor_p <- with(cor_dat, cor.test(age, AU05))
qplot(x = age, y = AU05, data = cor_dat, color = GROUP,
      geom = c("point", "smooth"), method = "lm",
      xlab = "Daughter Age (Years)",
      ylab = "Action Unit 5 Correspondence")
```

## Action Unit 6

```{r}
# Correlation of child age with AU06 correspondence
cor_p <- with(cor_dat, cor.test(age, AU06))
qplot(x = age, y = AU06, data = cor_dat,
      geom = c("point", "smooth"), method = "lm",
      xlab = "Daughter Age (Years)",
      ylab = "Action Unit 6 Correspondence") +
  annotate("text", x = 13.5, y = .6,
           label = paste0("r = ", round(cor_p$estimate, 2), 
                          "\np = ", round(cor_p$p.value, 3)), size = 5) +
  scale_x_continuous(breaks = 13:18) +
  theme_minimal(base_size = 18)

# Look at age-positive affect correspondence correlations within groups 
with(cor_dat %>% filter(GROUP=="control"), cor.test(AU06, age, method = "pearson"))
with(cor_dat %>% filter(GROUP=="depressed"), cor.test(AU06, age, method = "pearson"))
with(cor_dat %>% filter(GROUP=="self-harm"), cor.test(AU06, age, method = "pearson"))
```

```{r}
cor_p <- with(cor_dat, cor.test(age, AU06))
qplot(x = age, y = AU06, data = cor_dat, color = GROUP,
      geom = c("point", "smooth"), method = "lm",
      xlab = "Daughter Age (Years)",
      ylab = "Action Unit 6 Correspondence")
```

## Action Unit 9

```{r}
# Correlation of child age with AU09 correspondence
cor_p <- with(cor_dat, cor.test(age, AU09))
qplot(x = age, y = AU09, data = cor_dat,
      geom = c("point", "smooth"), method = "lm",
      xlab = "Daughter Age (Years)",
      ylab = "Action Unit 9 Correspondence") +
  annotate("text", x = 13.5, y = .6,
           label = paste0("r = ", round(cor_p$estimate, 2), 
                          "\np = ", round(cor_p$p.value, 3)), size = 5) +
  scale_x_continuous(breaks = 13:18) +
  theme_minimal(base_size = 18)

# Look at age-positive affect correspondence correlations within groups 
with(cor_dat %>% filter(GROUP=="control"), cor.test(AU09, age, method = "pearson"))
with(cor_dat %>% filter(GROUP=="depressed"), cor.test(AU09, age, method = "pearson"))
with(cor_dat %>% filter(GROUP=="self-harm"), cor.test(AU09, age, method = "pearson"))
```

```{r}
cor_p <- with(cor_dat, cor.test(age, AU09))
qplot(x = age, y = AU09, data = cor_dat, color = GROUP,
      geom = c("point", "smooth"), method = "lm",
      xlab = "Daughter Age (Years)",
      ylab = "Action Unit 9 Correspondence")
```

## Action Unit 10

```{r}
# Correlation of child age with AU10 correspondence
cor_p <- with(cor_dat, cor.test(age, AU10))
qplot(x = age, y = AU10, data = cor_dat,
      geom = c("point", "smooth"), method = "lm",
      xlab = "Daughter Age (Years)",
      ylab = "Action Unit 4 Correspondence") +
  annotate("text", x = 13.5, y = .6,
           label = paste0("r = ", round(cor_p$estimate, 2), 
                          "\np = ", round(cor_p$p.value, 3)), size = 5) +
  scale_x_continuous(breaks = 13:18) +
  theme_minimal(base_size = 18)

# Look at age-positive affect correspondence correlations within groups 
with(cor_dat %>% filter(GROUP=="control"), cor.test(AU10, age, method = "pearson"))
with(cor_dat %>% filter(GROUP=="depressed"), cor.test(AU10, age, method = "pearson"))
with(cor_dat %>% filter(GROUP=="self-harm"), cor.test(AU10, age, method = "pearson"))
```

```{r}
cor_p <- with(cor_dat, cor.test(age, AU10))
qplot(x = age, y = AU10, data = cor_dat, color = GROUP,
      geom = c("point", "smooth"), method = "lm",
      xlab = "Daughter Age (Years)",
      ylab = "Action Unit 10 Correspondence")
```

## Action Unit 12

```{r}
# Correlation of child age with AU12 correspondence
cor_p <- with(cor_dat, cor.test(age, AU12))
qplot(x = age, y = AU12, data = cor_dat,
      geom = c("point", "smooth"), method = "lm",
      xlab = "Daughter Age (Years)",
      ylab = "Action Unit 4 Correspondence") +
  annotate("text", x = 13.5, y = .6,
           label = paste0("r = ", round(cor_p$estimate, 2), 
                          "\np = ", round(cor_p$p.value, 3)), size = 5) +
  scale_x_continuous(breaks = 13:18) +
  theme_minimal(base_size = 18)

# Look at age-positive affect correspondence correlations within groups 
with(cor_dat %>% filter(GROUP=="control"), cor.test(AU12, age, method = "pearson"))
with(cor_dat %>% filter(GROUP=="depressed"), cor.test(AU12, age, method = "pearson"))
with(cor_dat %>% filter(GROUP=="self-harm"), cor.test(AU12, age, method = "pearson"))
```

```{r}
cor_p <- with(cor_dat, cor.test(age, AU12))
qplot(x = age, y = AU12, data = cor_dat, color = GROUP,
      geom = c("point", "smooth"), method = "lm",
      xlab = "Daughter Age (Years)",
      ylab = "Action Unit 12 Correspondence")
```

## Action Unit 25

```{r}
# Correlation of child age with AU25 correspondence
cor_p <- with(cor_dat, cor.test(age, AU25))
qplot(x = age, y = AU25, data = cor_dat,
      geom = c("point", "smooth"), method = "lm",
      xlab = "Daughter Age (Years)",
      ylab = "Action Unit 4 Correspondence") +
  annotate("text", x = 13.5, y = .6,
           label = paste0("r = ", round(cor_p$estimate, 2), 
                          "\np = ", round(cor_p$p.value, 3)), size = 5) +
  scale_x_continuous(breaks = 13:18) +
  theme_minimal(base_size = 18)

# Look at age-positive affect correspondence correlations within groups 
with(cor_dat %>% filter(GROUP=="control"), cor.test(AU25, age, method = "pearson"))
with(cor_dat %>% filter(GROUP=="depressed"), cor.test(AU25, age, method = "pearson"))
with(cor_dat %>% filter(GROUP=="self-harm"), cor.test(AU25, age, method = "pearson"))
```

```{r}
cor_p <- with(cor_dat, cor.test(age, AU25))
qplot(x = age, y = AU25, data = cor_dat, color = GROUP,
      geom = c("point", "smooth"), method = "lm",
      xlab = "Daughter Age (Years)",
      ylab = "Action Unit 25 Correspondence")
```

```{r include=FALSE}
rm(cor_dat)
rm(cor_p)
```
